### 2018-10-16 Latex/ArticleNew.tex
Second revision by Erik

We have carried out a theoretical and numerical investigation of SW wave turbulence. First, we derived the SW analogue (\ref{eq_Kolmo}) of the the `four-fifths' law of Kolmogorov turbulence. Using this relation and straightforward statistical and geometrical arguments we developed a simple shock model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3} $, where $ d $ is the mean distance between the shocks, and that the $ p $:th order structure function above a certain minimum will scale as $ (\epsilon d)^{p/3} r/d $. Then, we carried out a series of twenty forced dissipative simulations, varying the Froude number and the resolution. In all simulations, a statistically stationary state were reached and in all simulations we observed shocks. The flow variables in each Fourier mode was found to evolve as a linear wave, with equipartition between APE and KE over a period. The third order structure function relation was fulfilled with a high degree of accuracy. From the simulations we made two interesting observations that fall outside the predictive range of the model. The first observation  was  that mean energy in the stationary state approximately scales as (\ref{MeanEnergy}), suggesting that the normalised dissipation (\ref{Dissipation}) will go to zero both in the limit of small viscosity and large  wave speed. This is different from three dimensional Kolmogorov turbulence as well as strongly stratified turbulence, where, in both cases, dissipation is finite in the limit of small viscosity, and in the latter case also is independent of the degree of stratification. This observation suggests that SW wave turbulence does not fit into the paradigm of a local Richardson-Kolmogorov cascade. The second observation we made was that the mean distance between the shocks scales as $ c^{-1/2} $, if the other parameters are held constant. As we increased $ c $, the shocks were thus becoming denser. Using this observation we tested the shock model by plotting the normalised and compensated structure functions of different orders. Generally we found that there was a quite good agreement between the simulation results and the model predictions, becoming better with decreasing  wave speed and increasing resolution.

Combining the model and the observations we can get a quite good picture of the dynamics in the limit of weak nonlinearities, $ F_{f} \rightarrow  0 $.  
The picture may become more vivid if we say `wave breaking' were we previously have talked about shock formation, and also say
`wave lengths' were we previously have talked about length scales. We identify the longest wave length, $ \lambda_l $,  with the forcing scale $  L_f $ and the breaking wave length, $ \lambda_b $, with the mean distance, $ d $, between the shocks. There are two dynamically different  regimes to consider, the short wave  regime, $ [\delta x, \; \lambda_b] $, and the long wave regime, $ [\lambda_b, \, \lambda_l] $. We first consider the latter, whose width scales  $ \lambda_{l} /\lambda_b \sim F_f^{-1/2} $. Identifying the amplitude of the breaking waves with the shock amplitude, $ (\eps d)^{1/3} $, we find that the ratio between the amplitude of the longest waves and the breaking waves scales as $ E^{1/2}/(\eps d)^{1/3} \sim F_{f}^{-5/12} n^{\alpha/2} $, where we may substitute  $ n $ with a Reynolds number to some power.  Thus, for small $ F_f $ and large Reynolds number the longest waves are not directly influenced by wave breaking. The Reynolds number dependence of the amplitude ratio makes it unlikely that a general similarity theory can be easily formulated for this range. Therefore, predictions from weak turbulence theory \cite[for example][]{ZakharovSagdeev1970}
are not likely to hold for this range, although it is not directly influenced by wave breaking. The exact values of the power law exponents in the argument, are, of course, not important. As for the short wave regime, the width scales as $  \lambda_b /\delta x \sim F_f^{1/2} $ for fixed $ \delta x $ or fixed Reynolds number. As $ F_{f} \rightarrow 0 $ the range will eventually become so narrow so that breaking will disappear. On the other hand, it may be argued that wave breaking will take place for any small $ F_f $, provided that the Reynolds number is sufficiently large. Apparently, a necessary condition for wave breaking is that
\begin{equation} \label{NC}
\frac{\lambda_b}{\delta x} \sim \frac{\lambda_l F_f^{1/2}}{\delta x} \gg 1 \, .
\end{equation}
It may be interesting to note that the single point limit of the flatness factors shown if figure (\ref{fig_flatness}) scales as the ratio $ \lambda_b/\delta x $ and that this limit is equal to the flatness factor of velocity derivatives. So the condition (\ref{NC}) means that the flatness factor of velocity derivatives must be much larger than unity. Assuming that this is not only a necessary but also sufficient condition, we would able to formulate under what condition wave breaking will take place in terms of a Froude number and a Reynolds number if we knew how the shock width $ \delta x $ scales with these parameters.
In setting up the simulations we assumed that it is sufficient to resolve the Kolmogorov scale, $ \eta = (\nu^{3} / \epsilon)^{1/4} $, or the corresponding scale, $ \eta_8 = (\nu_8^{3}/\epsilon) ^{1/22} $, when hyperviscosity is used. The results from the simulations seem to support this assumption, suggesting that $ \delta x $ can be identified as the Kolmogorov scale.  Assuming that this is correct and defining the Reynolds number as $ Re \equiv \lambda_l^{4/3}\epsilon ^{1/3} /\nu $, we can write the condition for wave breaking as
\begin{equation} \label{Condition} 
Re^{3/4} Fr^{1/2} \gg 1 \, .
\end{equation} 
However, a little bit of reflection may lead us to doubt that the shock width is equal to the Kolmogorov scale. The reason for this is that dissipation only occurs at the shocks.
Using Navier-Stokes viscosity and assuming that the shock width is the characteristic dissipation length scale, the mean energy dissipation rate can be estimated as
\begin{equation}
\eps \sim \nu \frac{\mid \Delta u \mid ^2}{\delta x ^2} \frac{L_s \delta x}{\cal{A}} \sim \nu \frac{ \;\;\;  (\epsilon \lambda_b)^{2/3} }{\delta x \lambda_b} \, ,
\end{equation} 
where we have used the estimate (\ref{Strength}) for the shock amplitude. Consequently we obtain
\begin{equation} \label{ShockWidth}
\delta x \sim \frac{\eta^{4/3}}{\lambda_b^{1/3}} \sim \frac{\eta^{4/3}}{\lambda_l^{1/3}} F_f^{-1/6} \, ,
\end{equation} 
where we have used the observed scaling law (\ref{MeanDistance}) for $ \lambda_b = d $. An analogous result is obtained if we instead use hyperviscosity.  The estimate (\ref{ShockWidth}) suggests that $ \delta x $ should become somewhat larger  with increasing $ c $, but very slowly, $ \delta x \sim c^{1/6} $.  It is difficult to judge from the simulations  if this is actually the case. In figure (\ref{fig_spectra_c40}) we see that the maximum of the bottleneck in the high wave number end of the spectra appears at a somewhat smaller wave number in the run with largest $ c $ as compared to the two other runs. We leave it as an open question whether this is a signature of a slowly increasing shock width with increasing $ c $. It is interesting to note that if (\ref{ShockWidth}) is used as the estimate of $ \delta x $ in (\ref{NC}) instead of the Kolmogorov scale, we actually obtain the same condition (\ref{Condition}).

@@

Although the answer to the question that originally motivated this study is negative, it may lead us or some other investigators to pursue another interesting research direction. As pointed out in the introduction, the acoustic equations are to the lowest order expansion in density pertubations identical to the SW equations. This study may therefore give important clues to the long standing problem of acoustic turbulence, in two and three dimensions. A similar shock model as we developed in two dimensions may easily be formulated in three dimensions, where the third order structure function law will be  similar to (\ref{eq_Kolmo}), apart from the constant. In three dimensions we find
\begin{equation}
\meane{ |\delta \uu|^2 \delta J_L } 
+ c^2\meane{ (\delta h)^2 \delta u_L } = - \frac{8}{3} \varepsilon r. \label{eq_Kolmo3}
\end{equation}
 In the case of acoustic turbulence $ \delta h $ should  be interpreted as a density increment rather than a displacement increment.  If shocks in  three dimensions are assumed to form as  smooth surfaces rather than smooth lines, then the mean distance, $ d $, between the shocks will appear in the model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total  shock area and $ \cal{V} $ is the volume of the domain. The shock amplitude will thus scale as $ (\epsilon d)^{1/3} $ and the structure functions will scale as $ (\epsilon d)^{p/3} r/d $ also in three dimensions, provided, of course, that shocks will form in a similar way as in two dimensions. If they do, the most interesting questions are if the mean energy and the mean distance between the shocks scale in a similar way in three dimensions as in two dimensions. Simulations or experiments of acoustic turbulence may provide answers to these questions -- answers that will lead to further clues to a theoretical understanding of acoustic turbulence. 
 We hope that the present study will stimulate research in this direction.

>>>>

We have carried out a theoretical and numerical investigation of SW wave turbulence. First, we derived the SW analogue (\ref{eq_Kolmo}) of the the `four-fifths' law of Kolmogorov turbulence. Using this relation and straightforward statistical and geometrical arguments we developed a simple shock model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3} $, where $ d $ is the mean distance between the shocks, and that the $ p $:th order structure function above a certain minimum will scale as $ (\epsilon d)^{p/3} r/d $. Then, we carried out a series of twenty forced dissipative simulations, varying the Froude number and the resolution. In all simulations, a statistically stationary state were reached and in all simulations we observed shocks. The flow variables in each Fourier mode were found to evolve in accordance with linear wave dynamics, with equipartition between APE and KE over a period. The third order structure function relation was fulfilled with a high degree of accuracy. From the simulations we made two interesting observations that fall outside the predictive range of the model. The first observation  was  that mean energy in the stationary state approximately scales as (\ref{MeanEnergy}), suggesting that the normalised dissipation (\ref{Dissipation}) will go to zero both in the limit of small viscosity and large  wave speed. This is different from three dimensional Kolmogorov turbulence as well as strongly stratified turbulence, where, in both cases, dissipation is finite in the limit of small viscosity, and in the latter case also is independent of the degree of stratification. This observation suggests that SW wave turbulence does not fit into the paradigm of a local Richardson-Kolmogorov cascade. The second observation we made was that the mean distance between the shocks scales as $ c^{-1/2} $, if the other parameters are held constant. As we increased $ c $, the shocks were thus becoming denser. Using this observation we tested the shock model by plotting the normalised and compensated structure functions of different orders. Generally we found that there was a quite good agreement between the simulation results and the model predictions, becoming better with decreasing  wave speed and increasing resolution.

Combining the model and the observations we can get a quite good picture of the dynamics in the limit of weak nonlinearities, $ F_{f} \rightarrow  0 $.  
The picture may become more vivid if we say `wave breaking' were we previously have talked about shock formation, and also say
`wave lengths' were we previously have talked about length scales. We identify the longest wave length, $ \lambda_l $,  with the forcing scale $  L_f $ and the breaking wave length, $ \lambda_b $, with the mean distance, $ d $, between the shocks. There are two dynamically different  regimes, the short wave  regime, $ [\delta x, \; \lambda_b] $, and the long wave regime, $ [\lambda_b, \, \lambda_l] $. We first consider the latter, whose width scales  $ \lambda_{l} /\lambda_b \sim F_f^{-1/2} $. Identifying the amplitude of the breaking waves with the shock amplitude, $ (\eps d)^{1/3} $, we find that the ratio between the amplitude of the longest waves and the breaking waves scales as $ E^{1/2}/(\eps d)^{1/3} \sim F_{f}^{-5/12} n^{\alpha/2} $, where we may substitute  $ n $ with a Reynolds number to some power.  Thus, for small $ F_f $ and large Reynolds number the longest waves are not directly influenced by wave breaking. The Reynolds number dependence of the amplitude ratio makes it unlikely that a general similarity theory can be easily formulated for this range. Therefore, predictions from weak turbulence theory \cite[for example][]{ZakharovSagdeev1970}
are not likely to hold for this range, although it is not directly influenced by wave breaking. The exact values of the power law exponents in the argument leading to this conclusion are, of course, not important. As for the short wave regime, the width scales as $  \lambda_b /\delta x \sim F_f^{1/2} $ for fixed $ \delta x $ or fixed Reynolds number. As $ F_{f} \rightarrow 0 $ the range will eventually become so narrow so that breaking will disappear. On the other hand, it may be argued that wave breaking will take place for any small $ F_f $, provided that the Reynolds number is sufficiently large, since the shock width $ \delta x $ is decreasing indefinitely with increasing Reynolds number.

@@

Although the answer to the question that originally motivated this study is negative, it may lead us or some other investigators to pursue another interesting research direction. As pointed out in the introduction, the acoustic equations are to the lowest order expansion in density pertubations identical to the SW equations. This study may therefore give important clues to the long standing problem of acoustic turbulence, in two and three dimensions. A similar shock model as we developed in two dimensions may easily be formulated in three dimensions, where the third order structure function law will be  similar to (\ref{eq_Kolmo}), with the only difference that the constant $ 4 $ on the right hand side should be replaced by $ 8/3 $. In three dimensions we find
\begin{equation}
\meane{ |\delta \uu|^2 \delta J_L } 
+ c^2\meane{ (\delta h)^2 \delta u_L } = - \frac{8}{3} \varepsilon r. \label{eq_Kolmo3}
\end{equation}
 In the case of acoustic turbulence $ \delta h $ should  be interpreted as a normalised density increment rather than a displacement increment.  If shocks in  three dimensions are assumed to form as  smooth surfaces rather than smooth lines, then the mean distance, $ d $, between the shocks will appear in the model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total  shock area and $ \cal{V} $ is the volume of the domain. The shock amplitude will thus scale as $ (\epsilon d)^{1/3} $ and the structure functions will scale as $ (\epsilon d)^{p/3} r/d $ also in three dimensions, provided, of course, that shocks will form in a similar way as in two dimensions. If they do, the most interesting questions are if the mean energy and the mean distance between the shocks scale in a similar way in three dimensions as in two dimensions. Simulations or experiments of acoustic turbulence may provide answers to these questions -- answers that will lead to further clues to a theoretical understanding of acoustic turbulence. 
 We hope that the present study will stimulate research in this direction.
